Quantum Hoare Type Theory

### 2020-06-09 ms-paper/ms-paper.tex
Add note for consequence of removal of conditional

\section{Teleportation}
\label{app:teleport}
\todo{TODO: Refine assertions}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi a : Qbit. \Pi e : Qbit
        {(Id(a, -) /\ entangled(e)}
           r : (Bool, Bool)
        {emp}
      = \a.\e.do applyU (ifQ a (X e));
                 applyU (H a);
                 (measQbit a, measQbit e)
\end{lstlisting}

\subsection{Bob's circuit}
\begin{lstlisting}[language=QHaskell]
bob : \Pi m1 m2 : Bool. \Pi e : Qbit
      {entangled(e)}
         r : Qbit
      {(Id(r, -)}
      = \m1.\m2.\e.do if m1 then applyU (Z e) else ();
                      if m2 then applyU (X e) else ();
                      return e
\end{lstlisting}

>>>>

\section{Teleportation}
\label{app:teleport}
\todo{TODO: Refine assertions}
\subsection{Alice's circuit}
\begin{lstlisting}[language=QHaskell]
alice : \Pi a : Qbit. \Pi e : Qbit
        {(Id(a, -) /\ entangled(e)}
           r : (Bool, Bool)
        {emp}
      = \a.\e.do applyU (ifQ a (X e));
                 applyU (H a);
                 return (measQbit a, measQbit e)
\end{lstlisting}

\subsection{Bob's circuit} \todo{TODO: With \texttt{if ... then ... else} removed, this will not work}
\begin{lstlisting}[language=QHaskell]
bob : \Pi m1 m2 : Bool. \Pi e : Qbit
      {entangled(e)}
         r : Qbit
      {(Id(r, -)}
      = \m1.\m2.\e.do if m1 then applyU (Z e) else ();
                      if m2 then applyU (X e) else ();
                      return e
\end{lstlisting}
